Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-27 manuscript.Rmd
Update file and directory structure in Rmd

# read in metric names
metrics <- t(read.csv("./results/primary/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])

# read in metrics from crq analyses (target filtered)
metrics_all_targ <- t(read.csv("./results/primary/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
metrics_pos_targ <- t(read.csv("./results/primary/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
metrics_neg_targ <- t(read.csv("./results/primary/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (target filtered)
sig_all_targ <- t(read.csv("./results/primary/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
sig_pos_targ <- t(read.csv("./results/primary/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
sig_neg_targ <- t(read.csv("./results/primary/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])

@@

# call image
knitr::include_graphics("./results/primary/crqa/target/rp-all_events.png")

@@

# call image
knitr::include_graphics("./results/primary/crqa/target/rp-pos_events.png")

@@

# call image
knitr::include_graphics("./results/primary/crqa/target/rp-neg_events.png")

>>>>

# read in metric names
metrics <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", header = FALSE)[-2,-1])

# read in metrics from crq analyses (target filtered)
metrics_all_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
metrics_pos_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
metrics_neg_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (target filtered)
sig_all_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_all.csv", header = FALSE)[-1,-1])
sig_pos_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_pos.csv", header = FALSE)[-1,-1])
sig_neg_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_neg.csv", header = FALSE)[-1,-1])

@@

# call image
knitr::include_graphics("./results/primary/crqa/target-rp-all_events.png")

@@

# call image
knitr::include_graphics("./results/primary/crqa/target-rp-pos_events.png")

@@

# call image
knitr::include_graphics("./results/primary/crqa/target-rp-neg_events.png")
